---
title: "About Data Science (HW1)"
format: html
editor: visual
---

## What do you think being a Data Scientist is about?

I think of a Data Scientist as an advanced Data Analyst. A Data Analyst tends to look at current data and pulls important insights and trends that help drive business decisions and solve problems. A Data Scientist takes that idea even further by performing predictive analytics using ML on large datasets to extract meaningful insights. 

## What differences/similarities do you see between data scientists and statisticians?

Both fields work in data but have a different approach. Data Scientists tend to focus on computational analysis of the data and data modeling while Statisticians focus on topics such as inference and statistical theory. 

* Data Scientist: Machine Learning, Big Data, Data Engineering, Python and R, tend to work in tech companies (finance, marketing, healthcare)

* Statisticians: Theoretical foundations of statistical methods, experimental design, hypothesis testing, probability theory, tend to work in research (e.g., pharmaceuticals). 

# How do you view yourself in relation to these two areas?

I view myself more towards a Data Scientist than a Statistician, mainly based on my past experience and career goals. I enjoy ML and modeling more than I enjoy doing research. I worked as a Product Analyst intern for a tech company before where I used softwares like Python, Tableau, and SQL to derive important insights. My goal is to work in some sort of a Data Analyst or Data Scientist role in the future. However, I do possess the knowledge of a Statistician as well since I did my Bachelor's in Statistics as well.

```{r}
y <- density(iris$Petal.Width)
```

```{r}
class(y)
typeof(y)
str(y)
```

```{r}
#| echo: FALSE
plot(y)
```














